---
title: "Group 4 Football Visualization( FC Barcelona 2008–2016 Analysis Shiny App)"
output: github_document
date: "2025-05-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




This Shiny dashboard is for visualization of European football with a focus of helping FC Baracelona prepare for 2017 season


### Prerequisites


1. **R** (version 4.0.0 or higher)
2. The file `data/all_obj_shiny.rda` must be in a folder named `data` at the project root.
3. **Internet access** (to install missing packages).



### Required R Packages

We’ll use the following packages:

```{r}

pkg_df <- read.csv("pkg_df.csv")
knitr::kable(pkg_df, caption = "Required R Packages for the Shiny App")
```

```{r}
packages <- pkg_df$Package
packages
```




### Setup Instructions

1. **Clone or download** this repository to your machine.

2.  Click .Rproj file to open the project in RStudio


3. **Install** the required packages by copying the helper function below into your R session (or at the top of your `app.R`), then run it:

   ```r
   installPackages <- function(pkgs) {
     for (pkg in pkgs) {
       if (!pkg %in% rownames(installed.packages())) {
         message(sprintf("Installing missing package: %s", pkg))
         install.packages(pkg, dependencies = TRUE)
       } else {
         message(sprintf("Package already installed: %s", pkg))
       }
       library(pkg, character.only = TRUE)
     }
   }

   # Run to install & load:
   installPackages(packages)
   ```

4. In R console  the following

   ```r
   library(shiny)
   runApp()
   ```



### Running via RStudio

1. In RStudio, open `ui.R or server.R or app.r` file in the editor pane.
2. Click the **Run App** button (top-right of the editor pane).
A new window or RStudio viewer pane will open with the dashboard.


